---
title: "R Notebook"
output:
  html_document:
    df_print: paged
params:
  out_prefix: 'E:/EpigenticDrift/Figures/Fig4'  
---



# a, The cumulative curves are plotted as the drift-CpG sites increase

```{r}
library(ggplot2)
library(dplyr)
d <- readRDS("Fig4a.rds")
p_cumu <- ggplot(usedplot, aes(x = x, y = mean, color=sample)) +
                geom_line() +
                labs(x="Number of CpGs", y="Cor ")+
                geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd , fill=sample), alpha = 0.3, color = NA)+
                scale_fill_manual(values = c("skyblue", "coral"), aesthetics = c("color", "fill"))+
                ggthemes::theme_few() +
                theme(axis.text.x = element_text(face="bold", size=15,color = "black"),
                      axis.text.y = element_text(size=15, face="bold", color = "black"),
                      axis.title.x =element_text(face="bold", size=15, color = "black", vjust = 0.1),
                      axis.title.y =element_text(face="bold", size=15, color = "black", vjust = 0.1)) +
                theme(plot.title = element_text(hjust=0.5, face="bold")) +
                theme(legend.text = element_text(color = "black", size = 15))  
p_cumu
date=format(Sys.time(), format="%B-%d-%y")
dir.create("Fig4")
ggsave(filename = paste0("Fig4/",date,"_cumulative_eds_cor",".pdf"),plot = p_cumu,width=6,height = 6)
```

# b,c,d, mapping EDS dynamics

```{r}
#### 4b 1 The changes in the mean and variance of  drift-CpGs between two observations of the same individual
data=readRDS('Fig4b_1.rds')
ggplot(data=data,aes(x=x,y=score))+
  geom_boxplot() +
  xlab('')+
  ylab('Mean of delta CpG')+
  ggtitle('')+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme_bw() +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        panel.grid.major=element_line(color="white"),
        panel.grid.minor=element_line(color="white"),
        panel.border=element_blank(),
        axis.line=element_line(color="black"),
        legend.title=element_blank(),
        legend.text = element_text(size=18),
        plot.title = element_text(hjust = 0.5,size=24))
##### 4b 2
data=readRDS('Fig4b_2.rds')
ggplot(data=data,aes(x=x,y=score))+
  geom_boxplot() +
  xlab('')+
  ylab('Delta variance of CpG')+
  ggtitle('')+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme_bw() +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        panel.grid.major=element_line(color="white"),
        panel.grid.minor=element_line(color="white"),
        panel.border=element_blank(),
        axis.line=element_line(color="black"),
        legend.title=element_blank(),
        legend.text = element_text(size=18),
        plot.title = element_text(hjust = 0.5,size=24))
####  4c, Histograms of the bootstrap sampling distributions of the NSPT delta mean and delta variance
p1=ggplot()+
  geom_histogram(data = delta_mean ,aes(x=delta_mean,y = ..count../sum(..count..)),bins = 15,alpha=0.6,fill='black',color='black')+
  xlab('Delta mean')+
  ylab('Frequency')+
  geom_vline(xintercept = 5.9e-3, colour="#990000")+
  geom_vline(xintercept = 0.00532837942631393, colour="black", linetype="dashed")+
  geom_vline(xintercept = 0.033023764805627, colour="black", linetype="dashed")+
  theme_bw()+
  theme(axis.text = element_text(size=18),
        axis.title = element_text(size=22))
p2=ggplot()+
  geom_histogram(data = delta_var ,aes(x=delta_var,y = ..count../sum(..count..)),bins = 15,alpha=0.6,fill='black',color='black')+
  xlab('Delta variance')+
  ylab('Frequency')+
  geom_vline(xintercept = 1.3e-4, colour="#990000")+
  geom_vline(xintercept = -0.00179147966939154, colour="black", linetype="dashed")+
  geom_vline(xintercept = 0.00406748614661749, colour="black", linetype="dashed")+
  theme_bw()+
  theme(axis.text = element_text(size=18),
        axis.title = element_text(size=22))

p1+p2

#### 4d,  Boxplot and scatter plot illustrate the changes in individual EDS with respect to age
data=readRDS('Fig4d.rds')
ggplot(data=data,aes(x=label,y=EDS))+
  geom_boxplot() +
  xlab('')+
  ylab('EDS')+
  ggtitle('')+
  theme_bw() +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        panel.grid.major=element_line(color="white"),
        panel.grid.minor=element_line(color="white"),
        panel.border=element_blank(),
        axis.line=element_line(color="black"),
        legend.title=element_blank(),
        legend.text = element_text(size=18),
        plot.title = element_text(hjust = 0.5,size=24))        
```

# e, The Venn diagram illustrates the overlap between CpG sites constituting EDS and CpG sites constituting published aging-related indicators

```{r}
library(ggVennDiagram)
library(RColorBrewer)
a <- readRDS("Fig4e.rds")
p <- ggVennDiagram(a, label = "count", edge_size = 2) + scale_fill_distiller(palette = "Pastel1")
date=format(Sys.time(), format="%y-%b-%d")
dir.create("fig4")
ggsave(filename = paste0('Fig4/',date,'_scoreVS_eds230_ggVennDiagram.pdf'),plot = p, width=8,height = 8)
```

# f,g The heatmap shows the consistency between EDS and the association with published age-related indicators

```{r}
library(corrplot)
usedplot1 <- readRDS("Fig4f.rds")
usedplot2 <- readRDS("Fig4g.rds")
pdf("Fig4/merge_scoreVS_heatmap.pdf", width=8, height=8)
corrplot(as.matrix(usedplot1$nspt_cor), is.corr = FALSE, type = 'lower', method = 'color', addCoef.col = 'black',     number.cex=1,
                 cl.lim=c(0,1), col=colorRampPalette(c("white","red"))(200),
                 tl.col = "black",
                 tl.cex = 1,
                 title = "NSPT")
#cor_CAS
corrplot(as.matrix(usedplot2$cas_cor), is.corr = FALSE,  add=T, type = 'upper', method = 'color', addCoef.col = 'black', number.cex=1,
             cl.lim=c(0,1), col=colorRampPalette(c("white","red"))(200),
             tl.col = "black",
             tl.cex = 0.8,
             title = "CAS")
dev.off()
```

# h The EDS of exceptionally long-lived individual and different age groups were compared using boxplot

```{r}
library(dplyr)
library(ggplot2)
usedplot_group <- readRDS("Fig4h.rds")
HMcolors <- scales::hue_pal()(5)
names(HMcolors) <- c("<20","20-40", "40-60", "60-90", "103")
p_boxscatte <- ggplot(data=usedplot_group,aes(x=group,y=eds, fill = group)) +
                    geom_violin(alpha=0.4, position = position_dodge(width = .75),size=1,color="black") +
                    geom_boxplot(notch = TRUE,  outlier.size = -1, color="black",lwd=0.5, alpha = 0.5)+
                    geom_point( shape = 21,size=1, position = position_jitterdodge(),alpha=0.5)+
                    scale_fill_manual(values = HMcolors)  +
                    ggthemes::theme_few() +
                    labs(x="Age") +
                    theme(axis.text.x = element_text(vjust = 1, face="bold", size=15,color = "black"),
                              axis.text.y = element_text(size=15, face="bold", color = "black"),
                              axis.title.x =element_text(face="bold", size=15, color = "black", vjust = 0.1),
                              axis.title.y =element_text(face="bold", size=15, color = "black"),
                              axis.ticks.length.x=unit(0.3, "cm"),
                              axis.ticks.length.y=unit(0.3, "cm"),
                              axis.ticks.x=element_line(color="black",size=1,lineend = 8),
                              axis.ticks.y=element_line(color="black",size=1,lineend = 8)) +
                    theme(plot.title = element_text(hjust=0.5, face="bold")) +
                    theme(# Hide panel borders and remove grid lines
                              #panel.border = element_blank(),
                              panel.border = element_rect(fill=NA,color="black", size=2, linetype="solid"),
                              panel.grid.major = element_blank(),
                              panel.grid.minor = element_blank(),
                              axis.line = element_line(colour = "black"))

dir.create("Fig4")
date=format(Sys.time(), format="%B-%d-%y")
ggsave(filename = paste0('Fig4/', date, 'p_box_EDS_centunarian.pdf'),plot = p_boxscatter, width=8,height = 8)
```
